\documentclass{article}
\usepackage{bubblecv}

\begin{document}

%\pagecolor{lightgray}


\begin{cv}[ljus utsläppt sida 2]{Gustav Svennas}{Curriculum Vitae}


\cvsection[summary]{Profile}  %-----------------------------------------------------------
I am a sport- and technology interested student who will at the start of September get a bachelor's degree in Computer Science. As a person I am usually described as patient, attentive, and helpful. I am a proficient worker both in group and alone, but prefer working in a team with colleagues. I have, among other sports, played hockey for 20 years, where both individual and team performance is important. Earlier employments can attest that I am willing to work, can take criticism, and often try to see the positive side of things.  


\cvsection[work]{Work experience} %------------------------------------------------------

\begin{cvevent}[2022-07][2022-08]
    \cvname{Office service}
    \cvdescription{Riksidrottsförbundet, Stockholm}
    \begin{itemize}
        \item Responsible for maintenance of the office.
    \end{itemize}
\end{cvevent}


\begin{cvevent}[2021-03][2021-10]
    \cvname{Update of the inventory systems}
    \cvdescription{Klarna (IT-consultant via Academic Work), Stockholm}
    \begin{itemize}
        \item Responsible for updating several inventory systems used for computers, phones, and other units of employees. 
        \item Cooperated and had contact with colleagues from, among other countries, USA, Germany, and Australia.
    \end{itemize}
\end{cvevent}


\begin{cvevent}[2015-06][2015-07]
    \cvname{Production worker}
    \cvdescription{Maquet Critical Care AB, Solna}
    \begin{itemize}
        \item Helped with preparing parts for assembly of different medical equipment.
    \end{itemize}
\end{cvevent}
%------------------------------------------------------

\cvsection[education]{Education}  %------------------------------------------------------

\begin{cvevent}[2023-04][2023-06]
    \cvname{Bachelor thesis, 16 credits}
    \cvdescription{Wexnet, Växjö, via Linköping University}
    \begin{itemize}
        \item Study where the tools GitHub, Azure Repos, Bitbucket, and GitLab for version control were compared and examined.
    \end{itemize}
\end{cvevent}

\begin{cvevent}[2018-09][2023-09]
    \cvname{Bachelor's degree studies, Computer Science}
    \cvdescription{Linköping University (study break in 2021)}
    \textbf{Courses:}
    \begin{itemize}
        \item Computer Hardware and Architecture, Software Engineering Theory, AI, Cybersecurity, and more.
        \item Object Oriented- and Concurrent Programming. 
        \item Algorithms, Programming Paradigms, and Operating Systems.
    \end{itemize}
\end{cvevent}
%----------------------------------------

\cvsection[menu]{Other experiences} %------------------------------------------------------

\begin{cvevent}[2017-06][2020-06]
    \cvname{Webmaster and Sports Director}
    \cvdescription{Linköping University Hockey Club}
\end{cvevent}

%------------------------------------------------------

\cvsidebar %-----------------------------------------------------------------------------


\cvsection[contact]{Contact}  %----------------------------------------------------------

\begin{cvitem}[Envelope][4]
    \textbf{Mail}\\
    \href{mailto:gustavsvennas@gmail.com}{\texttt{gustavsvennas@gmail.com}}
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Globe][4]
    \textbf{LinkedIn}\\
    \href{https://www.linkedin.com/in/gustav-svennas-18b575159}{\texttt{Gustav Svennas}}
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Phone][4]
    \textbf{Phone}\\
    \href{tel:+46702968266}{\texttt{070 296 82 66}}
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Home][4]
    \textbf{Address}\\
    Tullingebergsvägen 8C\\ 146 45 Tullinge
\end{cvitem}

\cvseparator[3]
\begin{cvitem}[Globe][4]
    \textbf{GitHub}\\
    \href{https://github.com/Svennas}{\texttt{Svennas}}
\end{cvitem}

%-----------------------------------------------------------


\cvsection[program]{Programming}  %-------------------------------------------------

\begin{cvitem}
    C++ (Good knowledge)
\end{cvitem}

\begin{cvitem}
    C (Good knowledge)
\end{cvitem}

\begin{cvitem}
    Java (Good knowledge)
\end{cvitem}

\begin{cvitem}
    Python (Basic knowledge)
\end{cvitem}

\cvseparator
\begin{cvitem}
    Matlab (Basic knowledge)
\end{cvitem}

\cvseparator
\begin{cvitem}
    Bash Scripting (Beginner)
\end{cvitem}
%-----------------------------------------------------------

\cvsection[skills]{Skills}  %-----------------------------------------------------------

\cvseparator
\begin{cvitem}
    Git (Basic)
\end{cvitem}



\cvseparator
\begin{cvitem}
    Linux, Kubuntu och Mint (Good experience)
\end{cvitem}

\cvseparator
\begin{cvitem}
    Windows 7 och 10 (Good experience)
\end{cvitem}

\cvseparator
\begin{cvitem}
    MacOS (Basic)
\end{cvitem}

\cvseparator
\begin{cvitem}
    Jira (Some experience)
\end{cvitem}

\cvseparator
\begin{cvitem}
    Driving license, categorie B
\end{cvitem}


\cvsection[languages]{Languages}  %--------------------------------------------------------

\cvskill{Swedish}{Native Language}{1.0}
\cvskill{English}{Fluently}{0.95}
%--------------------------------------------------------


\cvsection[dance][1.8]{Interests}  %--------------------------------------------------------

\cvseparator
\begin{cvitem}
    Golf
\end{cvitem}

\cvseparator
\begin{cvitem}
    Hockey 
\end{cvitem}

\cvseparator
\begin{cvitem}
    Hiking
\end{cvitem}

\cvseparator
\begin{cvitem}
    Social dance
\end{cvitem}

\cvseparator
\begin{cvitem}
    Board- and computer games
\end{cvitem}


\end{cv}

\end{document}
